Supporting Information

### 2018-03-28 SupportingInformation.Rmd
teststats plot done with same format and etc.

#convert to a copula and plot
pdf("./Results/SoilCNcop.pdf")
v_CN<-getcopula(d=d,rankon=T,ploton=T) 
dev.off()
```
<!--Shya please insert an automatic reference to the methods section "Model selection approach" at the location YYY above. I could not easily find a way to do section references by number that was consistent with the figure and table reference system you already have, but perhaps I missed it. In the end I think we will need to be able to refer to sections as well as figures and tables by number. I can see there is a package called "bookdown" that may help but there may be something easier using similar tools to what you have already used for figures and tables.-->
![Plot of the raw soil C and N data.\label{fig_soilCNraw}](./Results/SoilCNraw.pdf){ width=30%, height=30% }

@@

For a bivariate dataset $(x_i,y_i)$ for $i=1,...,n$, model selection involved several steps, 
most implemented using tools from the `VineCopula` package. Code combining these tools is in the
[`OurBiCopSelect`](https://github.com/sghosh89/BIVAN/blob/master/OurBiCopSelect.R) function and its dependencies in the [`BIVAN`](https://github.com/sghosh89/BIVAN) repository. 
<!--Shya, links to code are a good idea! Thanks for figuring this out and adding, we should do something like this in other methods sections.-->

@@

The third step of model selection was to fit multiple bivariate copula families to the ranked data $(u_i,v_i)$ via maximum likelihood, using the `BiCopEst` function in `VineCopula`. Families considered (with abbreviations and numeric codes here indicated) included the **N**ormal/Gaussian {1}, **C**layton {3}, **G**umbel {4}, **F**rank {5}, **J**oe {6}, **BB1** {7}, **BB6** {8}, **BB7** {9}, **BB8** {10}, **S**urvival **C**layton {13}, **S**urvival **G**umbel {14}, **S**urvival **J**oe {16}, **S**urvival **BB1** {17}, **S**urvival **BB6** {18}, **S**urvival **BB7** {19} and **S**urvival **BB8** {20} copulas.
Akaike Information Criterion (AIC) and Bayesian Information Criterion (BIC) values and accompanying model weights ($\text{AIC}_{\text{w}}$, $\text{BIC}_{\text{w}}$) were generated using standard formulas @burnham2003_modelselection. 
Descriptions of these copula families can be found in introductory texts on copulas @nelsen2007_copula
<!--Shya to please insert references for the book on copulas by Joe - it is on my desk, come get it please-->
and in references cited in `VineCopula`. The lower- and upper-tail dependence of the 
best-fitting member of each family was also provided by `BiCopEst`.

@@

<!--The message=F and warning=F flags are to suppress warnings that come when you pass a parameter
of 0 to the Frank or Clayton copulas. These are technicallly boundary cases for these families.
They correspond to the independent copula. The packages we use provide the indepdent copula, but
issue a warning. Since anyway we want the independent copula, we can suppress the warning. We ran this
without the warning and it is OK to supress it.-->
```{r stat_testing_save_result, message=F, warning=F, echo=F, cache=T, cache.extra=list(seed,mtime("TestStats_multivar_dataset.R"),mtime("CopupulaFunctions.R"),mtime("CopulaFunctions_flexible.R"))}
set.seed(seed)

@@

<!--Shya to edit the prentation below to make it more parallel to the presentation of the model selection results for C/N data above-->

>>>>

#convert to a copula and plot
pdf("./Results/SoilCNcop.pdf")
v_CN<-getcopula(d=d,rankon=T,ploton=T) 
dev.off()
```

![Plot of the raw soil C and N data.\label{fig_soilCNraw}](./Results/SoilCNraw.pdf){ width=30%, height=30% }

@@

For a bivariate dataset $(x_i,y_i)$ for $i=1,...,n$, model selection involved several steps, 
most implemented using tools from the `VineCopula` package. Code combining these tools is in the
[`OurBiCopSelect`](https://github.com/sghosh89/BIVAN/blob/master/OurBiCopSelect.R) function and its dependencies in the [`BIVAN`](https://github.com/sghosh89/BIVAN) repository.

@@

The third step of model selection was to fit multiple bivariate copula families to the ranked data $(u_i,v_i)$ via maximum likelihood, using the `BiCopEst` function in `VineCopula`. Families considered (with abbreviations and numeric codes here indicated) included the **N**ormal/Gaussian {1}, **C**layton {3}, **G**umbel {4}, **F**rank {5}, **J**oe {6}, **BB1** {7}, **BB6** {8}, **BB7** {9}, **BB8** {10}, **S**urvival **C**layton {13}, **S**urvival **G**umbel {14}, **S**urvival **J**oe {16}, **S**urvival **BB1** {17}, **S**urvival **BB6** {18}, **S**urvival **BB7** {19} and **S**urvival **BB8** {20} copulas.
Akaike Information Criterion (AIC) and Bayesian Information Criterion (BIC) values and accompanying model weights ($\text{AIC}_{\text{w}}$, $\text{BIC}_{\text{w}}$) were generated using standard formulas @burnham2003_modelselection. 
Descriptions of these copula families can be found in introductory texts on copulas @nelsen2007_copula , @joe2014_dependence and in references cited in `VineCopula`. The lower- and upper-tail dependence of the 
best-fitting member of each family was also provided by `BiCopEst`.

@@

<!--The message=F and warning=F flags are to suppress warnings that come when you pass a parameter
of 0 to the Frank or Clayton copulas. These are technicallly boundary cases for these families.
They correspond to the independent copula. The packages we use provide the indepdent copula, but
issue a warning. Since anyway we want the independent copula, we can suppress the warning. We ran this
without the warning and it is OK to supress it.-->
<!-- The lines you are talking about appeared as message not as warning(actualy no warning appered for this chunk), so we have to set message=F here-->
```{r stat_testing_save_result, message=F, echo=F, cache=T, cache.extra=list(seed,mtime("TestStats_multivar_dataset.R"),mtime("CopupulaFunctions.R"),mtime("CopulaFunctions_flexible.R"))}
set.seed(seed)

@@
